Inefficient Concessions and Mediation

### 2021-01-18 draft.tex
Revisions of Section 2 and 3 up to when I realized that nc sep eqm is the same as the repeated game in Section 2

The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles. If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''

@@

\begin{theorem}
	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}=\de^{nc}$. A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give no concessions in period 0 and play Trust unless the other country defects to Fight.
	\label{theorem:1}
\end{theorem}
\emph{Proof}: See Appendix.
\\
In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small. This is representative of a case where countries have suspicions about each other, but proceed anyway.

@@

This type of separating equilibrium can exist for some sets of parameters. Since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0, we refer to such an equilibrium as a \emph{no-concessions separating equilibrium}. This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
\\
%This section could use some cleanup and streamlining
\\
{\bf \emph{Concessions Separating Equilibrium}}

>>>>

The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles. If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''

@@

\begin{theorem}
	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}=\de^{nc}$. A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give no concessions in period 0 and play Trust unless the other country defects to Fight.
	\label{theorem:1}
\end{theorem}
\emph{Proof}: See Appendix.
\\
In this equilibrium, two mutually distrustful countries behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small. This is representative of a case where countries have suspicions about each other, but proceed anyway.

\begin{corollary}
	The threshold patience level for a country to play Trust in a no-concessions separating equilibrium, $\de_h^{nc}$, is higher than for the grim-trigger repeated game equilibrium. 
	\label{corollary:1}
\end{corollary}
\emph{Proof}: See Appendix.

@@

\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
High-type welfare under the no-concessions separating equilibrium is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D) \right\} = \frac{1}{1-\de_h}\left\{pT + (1-p)\left[W-D + \de_h(W-D)\right]\right\}$$
High-type welfare under the grim trigger repeated game equilibrium is $\frac{1}{1-\de_h}\left\{pT + (1-p)\left[-D + \de_h(W-D) \right]\right\}$
When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
%This type of separating equilibrium can exist for some sets of parameters. Since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0, we refer to such an equilibrium as a \emph{no-concessions separating equilibrium}. This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
\\
\\
{\bf \emph{Concessions Separating Equilibrium}}
